### 2016-05-03 text/building_path_conditions.tex
Add all comments from third reviewer.

@@

DSLTrans rules allow for dependencies to be specified on which elements of the
output model were created from specific elements of the input model. To resolve
these dependencies, traceability information for the transformation is created
during the execution of a DSLTrans model transformation~\cite{DBLP:conf/sle/BarrocaLAFS10}.
In our verification approach, we store this same information as symbolic \emph{traceability links}, in
order to record which elements belong to the same DSLTrans rule.

@@

An example of the symbolic traceability link creation process is shown in
\cref{fig:trace_links}. Note that symbolic traceability links are a solid line between
match and apply elements in our visual notation.

@@

@@

A new set of path conditions will then be created by sequentially combining each rule in the layer with the path condition selected. Recall that a path condition represents a set of rules that have symbolically executed, thereby abstracting a set of transformation executions through our abstraction relation. Combining a path condition with a rule will produce one or more path conditions depending on how the rule combines with the rules already represented by the path condition. The pre- and post- conditions defined by the path condition will be modified according to the elements found in that rule.

@@

@@

The below figures will demonstrate the four cases above. As a reminder of visual notation, the backward links are dashed lines between the match and apply graphs of the rule and path condition, while symbolic traceability links are solid lines between the two graphs.

@@

@@

>>>>

\reviewer{In Section 4, rather than starting first with the construction of path conditions
(Section 4,4), it would be more natural to discuss their meaning in terms of
transformation executions (Section 5), since that should be the justification for
your constructions.}

@@

DSLTrans rules specify which elements of the
output model were created from specific elements of the input model. To resolve
these dependencies, traceability information for the transformation is created
during the execution of a DSLTrans model transformation~\cite{DBLP:conf/sle/BarrocaLAFS10}.
In our verification approach, we store this same information as symbolic \emph{traceability links}, in
order to record which elements belong to the same DSLTrans rule.

@@

An example of the symbolic traceability link creation process is shown in
\cref{fig:trace_links}. Note that symbolic traceability links are solid lines between
match and apply elements in our visual notation.

@@

\reviewer{Def. 18 suddenly introduces the notion of “rule copies” (Rulecop) which are re-
ally not explained properly. My guess is that they are isomorphic representatives
of rules. On page 13 under ”notation” this component is called Rule and referred
to as a relation, and in Def. 28 it is denoted as Rules and required to be “the same
as the set of transformation rules used to build [the transformation execution]”
(and hence not isomorphic copies?). Needless to say, these inconsistencies do
not help understandability.}

@@

A new set of path conditions will then be created by sequentially combining each rule in the layer with the path condition selected. Recall that a path condition represents a set of rules that have symbolically executed, thereby abstracting a set of transformation executions through our abstraction relation. \reviewer{we cannot recall this as it has not yet been presented;
the abstraction relation is defined only in Section 5}Combining a path condition with a rule will produce one or more path conditions depending on how the rule combines with the rules already represented by the path condition. The pre- and post- conditions defined by the path condition will be modified according to the elements found in that rule.

@@

\reviewer{Def. 19 can only be understood once it is clear that your plan is to make iso-
morphic rule copies in which the node and edge identities already coincide with
those in your path condition. (Hence my “isomorphic representative” guess in
the previous remark.) This is very much nonstandard in the works of graph trans-
formation, and poorly motivated. What are the advantages of this approach over
relying on partial morphisms from a fixed rule to the path condition? As it is,
you have to explain that you only consider isomorphic copies that differ in rele-
vant parts, where “relevant” is determined by the question whether a node/edge
identity coincides with one on the path condition. (You actually do not explain
that at all: strictly following your definitions one would have to consider an in-
finite number of isomorphic rule copies, assuming that the number of available
identities is infinite (as it must be).)}

\reviewer{“joint” $\rightarrow$ “overlapping”? Why are the type graphs actually not
identical, as pc and rl are defined over the same source and target metamodels?
Last line: “rl” $\rightarrow$ “$\{rl\}$”}

@@

The figures below will demonstrate the four cases above. As a reminder of visual notation, the backward links are dashed lines between the match and apply graphs of the rule and path condition, while symbolic traceability links are solid lines between the two graphs.

@@

\reviewer{The right hand side of the conclusion of Def. 20 has $AC ∪ pc ′ ∈AC pc ′ $, of which
I cannot make sense. AC is a set, but the pc' are not, so what operation is
$\cup_{pc'\in AC} pc'$?}

\reviewer{Do you mean $\sqcup_{pc'\in AC}$instead? But then the result is not a set, so how can you take its union with AC? The same problem reoccurs in other definitions.}

@@

\reviewer{Def. 24: it seems to me you are making a very serious mistake here. $\blacktriangleright$ tests
for the existence of a morphism, but in Def. 19 you are relying on coincident node/edge identities. (See my remark 15.) Maybe you mean that the morphism from rl to pc should drive the choice of node/edge identity in the isomorphic copy of rl to be combined with pc, but this is really a wild guess on my part.}

### 2016-05-03 text/dsltrans.tex
Add reviewer's comments into the paper.
Add all comments from third reviewer.

@@

In \cref{fig:dsltransformation} we present a DSLTrans transformation that involves both metamodels.  A description of relevant constructs as well as visual notation remarks are found in \cref{subsec:DSLTrans_constructs}. Note
that the transformation is formed
from layers where each layer is a set of transformation rules. The
transformation will execute layer-by-layer, where transformation rules in a layer will execute in a
non-deterministic order but must produce a deterministic result, due to the fact that DSLTrans is confluent by construction~\cite{DBLP:conf/sle/BarrocaLAFS10}.

@@

The purpose of this \emph{Police Station} transformation is to flatten a chain of command given
in the \emph{Organization language} into two independent sets of male
and female officers represented in the \emph{Gender language}. The command
relations will be kept during this transformation, i.e. a female officer will
have a direct association to all her female subordinates and likewise for male
officers. Note that differences in the gender classification metamodel means
some relations present in the input model will not be retained in the output
model.

\begin{figure*}[htb]
        \centering
        \begin{subfigure}[b]{0.30\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/policestation_dsltrans/model_police_hierarchy.pdf}
                \caption{Original model}
                \label{fig:police_hierarchy}
        \end{subfigure}%
        ~~
        \begin{subfigure}[b]{0.40\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/policestation_dsltrans/model_police_gender.pdf}
                \caption{Transformed model}
                \label{fig:police_gender}
        \end{subfigure}%
        \caption{Model before and after transformation}
        \label{fig:transformationexample}
\end{figure*}

An example of this transformation's execution can be observed in \cref{fig:transformationexample}, where the input model is on the left and the output model is on the right. Notice that the elements $s$, $m_k$  and $f_k$ in \cref{fig:OrganizationLanguage} are instances of the source \emph{Organization} metamodel elements $Station$, $Male$ and $Female$ respectively. The primed elements in \cref{fig:GenderLanguage} are their counterpart instances in the target \emph{Gender} metamodel.

@@

As an example, consider the transformation rule marked \emph{Stations} in the
first rule layer in \cref{fig:dsltransformation}. The match graph holds
one \emph{Station} element from the source metamodel, while the apply graph
holds one \emph{Station} element from the target metamodel. This means that for all
elements in the input model which are of type \emph{Station} in the
\emph{Organization Language}, a element of type
\emph{Station} in the \emph{Gender Language} will be created in the output model.

Note that in our approach, we require that the match graph of a rule is not a subset of the match graph of any other rule (as formally stated in \cref{def:layer_transformation} of model transformation, in \cref{sec:formal_background} of this paper). This requirement is to prevent the case where a rule could not execute independently of another rule, except for the cases when such dependency is explicitly defined by backward links. This is undesirable for the algorithm as presented here as we will explain later. However, as seen in~\cite{conf/gg/SelimLCDO14}, the expressiveness of the transformations our algorithm can examine is not restricted. In that work, we detail an operational rule processing step to handle overlapping rules.

@@

In contrast, we do not expect the property in \cref{fig:dsltrans_prop2} to always hold. This property represents the statement ``\emph{any model which includes a
female officer will be transformed into a model where that female officer will
always supervise another female officer}''. It is not difficult to construct an input model where the pre-condition holds, but the post-condition does not. This would be an input model that contains only one female officer, as there will only be one female officer in the output model.

@@

\item \textbf{Indirect Match Links}: Indirect match links are similar to direct
match links, but there may exist a path of containment associations between the
matched instances. Our notion of indirect links captures only
acyclic EMF containment associations.

>>>>

\reviewer{Please explain, earlier on, the meaning of indirect edges.}

@@

In \cref{fig:dsltransformation} we present a DSLTrans transformation that involves both metamodels.  A description of relevant constructs as well as visual notation remarks are found in \cref{subsec:DSLTrans_constructs}. Note
that the transformation is formed
from layers where each layer is a set of transformation rules. The
transformation will execute layer-by-layer, where transformation rules in a layer will execute in a
non-deterministic order but will always produce a deterministic result, due to the fact that DSLTrans is confluent by construction~\cite{DBLP:conf/sle/BarrocaLAFS10}.

@@

The purpose of this \emph{Police Station} transformation is to flatten a chain of command given
in the \emph{Organization language} into two independent sets of male
and female officers represented in the \emph{Gender language}. The command
relations will be kept during this transformation, i.e. a female officer will
have a direct association to all her female subordinates and likewise for male
officers. Note that differences in the gender classification metamodel mean
some relations present in the input model will not be retained in the output
model.

\begin{figure*}[htb]
        \centering
        \begin{subfigure}[b]{0.30\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/policestation_dsltrans/model_police_hierarchy.pdf}
                \caption{Original model}
                \label{fig:police_hierarchy}
        \end{subfigure}%
        ~~
        \begin{subfigure}[b]{0.40\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/policestation_dsltrans/model_police_gender.pdf}
                \caption{Transformed model}
                \label{fig:police_gender}
        \end{subfigure}%
        \caption{Model before and after transformation}
        \label{fig:transformationexample}
\end{figure*}
\reviewer{Figure 3: I would suggest adding another node f5 superviesd by f4, to illustrate the
notion of transitive closure. Another remark: I think the black containment dia-
monds do not belong in an instance model, as they are a metamodel notion.}

An example of this transformation's execution can be observed in \cref{fig:transformationexample}, where the input model is on the left and the output model is on the right. Notice that the elements $s$, $m_k$  and $f_k$ in \cref{fig:OrganizationLanguage} are instances of the source \emph{Organization} metamodel elements $Station$, $Male$ and $Female$ respectively. The primed elements in \cref{fig:police_gender} are their counterpart instances in the target \emph{Gender} metamodel.

@@

As an example, consider the transformation rule marked \emph{Stations} in the
first rule layer in \cref{fig:dsltransformation}. The match graph holds
one \emph{Station} element from the source metamodel, while the apply graph
holds one \emph{Station} element from the target metamodel. This means that for all
elements in the input model which are of type \emph{Station} in the
\emph{Organization Language}, an element of type
\emph{Station} in the \emph{Gender Language} will be created in the output model.

Note that in our approach, we require that the match graph of a rule is not a subgraph of the match graph of any other rule (as formally stated in \cref{def:layer_transformation} of model transformation, in \cref{sec:formal_background} of this paper). This requirement is to prevent the case where a rule could not execute independently of another rule, except for the cases when such dependency is explicitly defined by backward links. This is undesirable for the algorithm as presented here as we will explain later. However, as seen in~\cite{conf/gg/SelimLCDO14}, the expressiveness of the transformations our algorithm can examine \reviewer{Perhaps 'the expressiveness of the rule language'?}  is not restricted. In that work, we detail an operational rule processing step to handle overlapping rules.

\reviewer{In page 10 (answer to the reviewers) you say that rules for a 
  layer must be parallel independent. Is this written anywhere in the
  main part of the paper? }

@@

\reviewer{Figure 4: The two “agent” edges in the postcondition should be marked “female”
resp. “male”} 
In contrast, we do not expect the property in \cref{fig:dsltrans_prop2} to always hold. This property represents the statement ``\emph{any model which includes a
female officer will be transformed into a model where that female officer will
always supervise another female officer}''. It is not difficult to construct an input model where the pre-condition holds, but the post-condition does not. For example, take an input model that contains only one female officer, as there will only be one female officer in the output model.

@@

\item \textbf{Indirect Match Links}: Indirect match links are similar to direct
match links, but there may exist a path of containment associations between the
matched instances. Our notion of indirect links captures only
acyclic EMF containment associations. \reviewer{“a nonempty path” (I think). The label of the
containment associations does not matter?}

### 2016-05-03 text/formal_background.tex
Add reviewer's comments into the paper.
Add all comments from third reviewer.

@@

@@

\CatchFileBetweenTags{\typedgraphhomomorphismtext}{text/definitions}{typedgraphhomomorphismtext}{\typedgraphhomomorphismtext}

@@

% \begin{lemma}{The Union of Two Typed Graph Homomorphisms is a Typed Graph Homomorphism}
% 
% Let $g=\langle V_g,E_g,st_g,\tau_g\rangle$, $g'=\langle
% V'_g,E'_g,st'_g,\tau'_g\rangle$, $h=\langle V_h,E_h,st_h,\tau_h\rangle$,
% $h'=\langle V'_h,E'_h,st'_h,\tau'_h\rangle$ be typed graphs, where $g$ and $h$
% are potentially joint, as well as $g'$ and $h'$. Let also $f:V_g\rightarrow V'_g$ and
% $i:V_h\rightarrow V'_h$ be a typed graph homomorphisms between $g$ and $g'$ and
% $h$ and $h'$, respectively. Let us show that $f\cup i$ is a typed graph homomorphism between $g\sqcup g'$ and $h\sqcup h'$.
% The proof is trivial if $g$ and $h$, as well as $h$ and $h'$ are disjoint. If $g$ and $h$ are joint over a vertex $v$, we know that $(f\cup i)(v)$
% \end{lemma}
% 
% \begin{lemma}{The Union of Two Surjective Typed Graph Homomorphisms is a Surjective Typed Graph Homomorphism}
% \levi{finish this proof}
% \end{lemma}

@@

@@

@@

@@

@@

@@

%Change if needed
\CatchFileBetweenTags{\inputoutputmodeltext}{text/definitions}{inputoutputmodeltext}{\inputoutputmodeltext}

@@

@@

@@

\begin{definition}{Expanded Transformation Rule\\}
\label{def:transformation_rule_expansion}
\CatchFileBetweenTags{\expandedtransformationrule}{text/definitions}{expandedtransformationrule}{\expandedtransformationrule}
\end{definition}
\CatchFileBetweenTags{\expandedtransformationruletext}{text/definitions}{expandedtransformationruletext}{\expandedtransformationruletext}

@@

@@

>>>>

\reviewer{Your formalisation is made more complex than necessary because you do not put
the power of typed graphs to work. If your source and target metamodels have
disjoint types (which you can assume without loss of generality) you can take
their union, augmented with trace edge types from all target node types to all
source node types, and take that to be the meta-model for an input-output model,
and also for a rule. Suddenly you don’t have to carry arround the distinction be-
tween Match and Apply (for rules) or input and output (for input-output models)
around any more: they are just the projections onto the types of the source, resp.
target metamodel.}

\reviewer{Section 4.2.2 on “backward links” is rather confusing, as it speaks about trace-
ability links being added to rules. You never add traceability links to rules any-
where in the paper; in fact, your formal notion of a rule has no room for them.
Instead, rules only have backward links. (The clarity of the the situation is not
improved by the fact that those are labelled trace.)}

\reviewer{I think the situation would be much more clear if you were to use the common
notion of left hand side and right hand side of a rule. The left hand side of a
rule rl is precisely your ||rl||, the right hand side is the entire rl augmented by
your traceability links, as in 4.2.2. Suddenly we are back in a well-known graph
transformation formalism, and your rules are in fact so simple (no deletion, no
negative application conditions, injective matching) that I believe it makes no
difference whether you use algebraic graph transformation or some more con-
structively defined variant. The only standard notion is that of transitive closure
in the left hand side; but there are plenty of GT tools that offer this extension.
In fact I see no reason why your rule application would then not precisely coin-
cide with the the same notion in, say, SPO graph rewriting; and I hope you agree
that this would help you no end in explaining what you are doing. (If, on the
other hand, there is after all some difference then this, too, would be interesting
to know, as that difference is not at all apparent right now.)}

\reviewer{Viewed like this, moreover, I think your notions of input-output models and rules
are very close to triple graph transformation as used by Schrr at all. I think the
main (if not only) difference lies in the fact that your "glue graph" is actually not
a graph; instead, you use traceability edges directly from the target model to the
source model. If you were to turn those edges into nodes with source and target
edges, even that difference would disappear.}

@@

\reviewer{There is a lot of redundancy in the paper, on several levels:
  - input-output-models, path conditions and properties are
    all defined very similarly. Couldn't you subsume them in a single
    definition and spell out the differences?}

@@

\reviewer{Graph union (Def. 2) is only well-defined if s $\cup$ s' , t $\cup$t' and $\tau \cup \tau$' yield functions,
which in turn is only the case if s and s' etc. coincide on common elements.
This is neither stated as a requirement here nor checked anywhere in the use of
the union. (Since I sure you implicitly had this restriction in mind, this may be
counted as sloppiness; you can probably assume this to hold w.l.o.g. wherever
you need it.)}
\CatchFileBetweenTags{\typedgraphhomomorphismtext}{text/definitions}{typedgraphhomomorphismtext}{\typedgraphhomomorphismtext}

@@

\reviewer{Def. 3 and all subsequent definitions g has an unexplained component st, is
this the same as the pair (s,t) in Def. 1?}

\reviewer{For multigraphs (which may contain parallel edges with the same label) it is
necessary to include edge images in the homomorphism (Def. 3). If you do not
do that, then graphs with parallel edges are isomorphic to graphs with single
edges (between the same nodes), so you might as well restrict to simple graphs.}

\reviewer{
Concretely: Right now the def. requires the existence of \textit{some} unfixed e' in the
target graph, but in fact \textit{f} should be extended to E $\rightarrow$ E' so that e' = f (e) in this
situation.
}
% \begin{lemma}{The Union of Two Typed Graph Homomorphisms is a Typed Graph Homomorphism}
% 
% Let $g=\langle V_g,E_g,st_g,\tau_g\rangle$, $g'=\langle
% V'_g,E'_g,st'_g,\tau'_g\rangle$, $h=\langle V_h,E_h,st_h,\tau_h\rangle$,
% $h'=\langle V'_h,E'_h,st'_h,\tau'_h\rangle$ be typed graphs, where $g$ and $h$
% are potentially joint, as well as $g'$ and $h'$. Let also $f:V_g\rightarrow V'_g$ and
% $i:V_h\rightarrow V'_h$ be a typed graph homomorphisms between $g$ and $g'$ and
% $h$ and $h'$, respectively. Let us show that $f\cup i$ is a typed graph homomorphism between $g\sqcup g'$ and $h\sqcup h'$.
% The proof is trivial if $g$ and $h$, as well as $h$ and $h'$ are disjoint. If $g$ and $h$ are joint over a vertex $v$, we know that $(f\cup i)(v)$
% \end{lemma}
% 
% \begin{lemma}{The Union of Two Surjective Typed Graph Homomorphisms is a Surjective Typed Graph Homomorphism}
% \levi{finish this proof}
% \end{lemma}

@@

\reviewer{Def. 6: Since the codomain of $\tau$ is apparently VT $\times$ {abstract, concrete} $\cup$ ET $\times$
{containment, reference}, it is certainly never going to be a bijection. However,
I think you actually only want injectiveness; what purpose is served by requiring
it to be surjective?}

\reviewer{As an aside, I think this is quite an awkward way to encode the notions of ab-
stractness and containment: I think it would be much more elegant to define
abstractness as a predicate over VT and containment as a predicate over ET. To
go even one step further, it would in fact be more natural (and more standard)
to equate the notions of type graph and metamodel altogether, as they certainly
serve the same conceptual purpose.
}

\reviewer{Def. 6 and many other places A word in math mode should always
be in $\backslash$mathit to avoid ugly spacing as in $re f erence$.}

@@

\reviewer{Def. 7: is an expanded metamodel a metamodel? Then you need to allow non-
injective $\tau$, at least on edges, as the requirement $\tau$(e) = $\tau$(e') in the third bullet
will certainly cause non-inejectiveness.}

@@

\reviewer{Def. 9 and many thereafter incrementally define new concepts on top of graphs.
Most of these definitions are rather hard to read, for several reasons:}

\begin{itemize}
\item It is common to use an unprimed version for the original object and a
primed version for the constructed object, whereas you turn this conven-
tion around
%\item Sloppiness: in more than 50 percent of all cases the ⊆ should be ⊇ or vice versa;
%in this particular instance, you really mean τ ′ ⊇ τ and E = E ′ ∪ E c ∗ .

\item It is really more readable to define the construction as a construction, so:
\begin{itemize}
\item  $E = E'\cup E^{\star}_{C}$
\item $s = s' \cup {(e_1 \dots e_n , s(e_1)) | e_1 \dots e_n \in E^{\star}_{C} }$
\item $t = t' \cup {(e_1 \dots e_n ,t(e_n )) | e_1 \dots e_n \in E^{\star}_{C} }$
\item $\tau = \tau' \cup {(e, indirect) | e \in E^{\star}_{C} }$
\end{itemize}
\begin{itemize}
\item Note that this also takes care of s and t, which you have forgotten here
and in all other similar definitions.)
\item The set $E^{\star}_{C}$should itself also be more carefully defined, as $E^{\star}_{C} = {e_1 \dots e_n \in E^∗' | \forall1 \leq i < n.t(e_i ) = s(e_{i+1} )}$
\end{itemize}
\end{itemize}

@@

\reviewer{Def. 10: Here you certainly should not require $\tau$ to be injective. The requirement
on containment relations is mathematical nonsense: if $e' \in E'$ has target b then
$b \in V'$ and so f (b) does not exist, and most certainly is not the source of any edge
in E. In fact, I really have no idea what you want to say here; the explanation
below the definition does not clarify matters at all.}

@@

\reviewer{“the cardinality of the target class”?? Are you talking about edge multiplicities here (which you have chosen not to include)?}

@@

\reviewer{Why is Input a model and Output a metamodel instance? Note that
$\backslash$ binds stronger than $\cup$ in $E \backslash E' \cup E$ ′′ . “match-apply patterns” → “input-output
patterns”}
%Change if needed
\CatchFileBetweenTags{\inputoutputmodeltext}{text/definitions}{inputoutputmodeltext}{\inputoutputmodeltext}

@@

\reviewer{e in $\tau(e) = \mathit{trace}$ is still bound by $\nexists$, so “and” should be $\land$}

@@

\reviewer{Def. 14: According to your own criterion, $||rl||$ is not a rule as it does not create
either a node or an edge.}

@@

\begin{definition}{Expanded Transformation Rule\\}
\label{def:transformation_rule_expansion}
\CatchFileBetweenTags{\expandedtransformationrule}{text/definitions}{expandedtransformationrule}{\expandedtransformationrule}
\end{definition}

\reviewer{The first bullet is a special case of the second, so can be removed.}
\CatchFileBetweenTags{\expandedtransformationruletext}{text/definitions}{expandedtransformationruletext}{\expandedtransformationruletext}

@@

\reviewer{The second half of Def. 16 raises a lot of questions. First of all, neither $\sqsubseteq 	 $ nor
$\cong$ are defined over rules; however, I can imagine what it would look like. Then,
what role does rl play; do you just mean $||rl_1 || \sqsubseteq ||rl_2 ||$ given a suitable isomorphic copy? What if $||rl_1 || \cong ||rl_2 || $(as a special case); is your condition then not
unsatisfiable as $rl_1$ must appear after $rl_2$ as well as vice versa?}

\reviewer{More importantly though, why do you care? Your semantics makes sure that
rules are never considered for application twice in succession, so dependencies
are always resolved unambiguously.}

@@

\reviewer{Definition 17: There is a copy/paste error w.r.t. Def. B.16 (which only serves to
strengthen my point, made above, about avoiding this kind of duplication). In
this case, B.16 is the correct version.}

### 2016-05-03 text/introduction.tex
Add all comments from third reviewer.

% This also provided us with performance gains over our
% previous implementation, due to the use of efficient graph-matching libraries to manipulate the graph structures required.

@@

>>>>

\reviewer{On Page 2, left, mid-page you state that your methods “differ from previous
work”in that you require no intermediate representation. It is certainly not preor-
dained that this difference is an advantage: such an intermediate representation
typically gives access to general-purpose tooling, e.g., for model checking or
theorem proving. You would have to argue that you are better off reimplement-
ing that functionality in your own setting. Is there any evidence for that? An
example of such evidence (in a somewhat different context) is for instance pro-
vided by Pennemann in his PhD thesis, where by experiments he shows that his
dedicated, graph-based resolution outperforms that of a general-purpose theorem
prover.}
% This also provided us with performance gains over our
% previous implementation, due to the use of efficient graph-matching libraries to manipulate the graph structures required.

@@

\reviewer{The paper is inconsistent (maybe due to the iteration of submitted versions) in
what it says about its own structure. Page 2, right, 1st paragraph states that the
language and its samentcs are presented in Section 2; Section 2 (1st paragraph)
says that the semantics is presented in Appendix B; most of it is actually in
Section 3. Appendix B indeed repeats essentially all of Section 3, a duplication
which certainly serves no purpose and should be remedied. In fact, I would much
prefer all of Appendix B to be moved to the main text, as the only part that is
now only in the appendix, the definition of a transformation, is absolutely central
to the paper.
As it currently stands, Section 3.4 has a similar problem: first it states that the
semantics is not in the main text, then it refers to Section 3.2 for the semantics
(which the reader has just gone through), then in Def. 17 jumps to a notation that
is only introduced in Appendix B.}
